---
title: "Lab 5A"
author: "Cassandra Richardson"
date: "4/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
lotr  <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/lotr_tidy.csv") |> 
  rename(Species = Race)
```

# Exercise 1: Univariate Pivoting 

```{r lotr}
View(lotr)
```
### After viewing this data, it would not be considered tidy for the analyses I would expect to conduct on it. For instance, I would consider each movie to be one observation, meaning that I would expect each movie to be represented once, with information about that movie in each column. To me, this data is too long. 

## Question 2. Widen the data so that we see the words spoken by each species, by putting species as its own column.

```{r pivot wide}
(lotr_wide <- lotr |> 
  pivot_wider(id_cols = c(Film, Gender), 
              names_from = Species, 
              values_from = Words))
```

## Question 3. Re-lengthen the wide LOTR from question 2. 

```{r pivot long}
lotr_wide |> 
  pivot_longer(cols = c(Elf, Hobbit, Man), 
               names_to  = "Species", 
               values_to = "Words")
```