---
title: "Lab 3"
author: "Cassandra Richardson"
date: "4/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(gapminder)
```

```{r table}
print(gapminder)
``` 

# Exercise 1 

## Part 1: Filter gapminder to three countries of my choice:

```{r dplyr 1.1}
gapminder_three <- gapminder |> 
  filter((country == "Iceland" | country == "Italy" | country == "Switzerland") & year >= 1970, year < 1980)
 print(gapminder_three)
```

## Part 2: Same as above, then select "country" and "gdpPercap"

```{r dplyr 1.2}
gapminder_three <- gapminder |> 
  filter((country == "Iceland" | country == "Italy" | country == "Switzerland") & year >= 1970, year < 1980) |>
  select(country, gdpPercap)
  print(gapminder_three)
```

## Part 3: Create a new variable for the change in life expectancy from the previous measurement for that country. Then filter to only show countries that experienced a drop in life expectancy. 

```{r dplyr 1.3}
lifeExp_decrease <- gapminder|>
  group_by(country) |>
  mutate(lifeExp_decrease = lifeExp - lag(lifeExp)) |>
  filter(lifeExp_decrease < 0)
  print(lifeExp_decrease)
```

## Part 4: Filter gapminder to show the max GDP per capita for each country 

```{r dplyr 1.4}

```

## Part 5: Create a scatterplot of Canda's life expectancy vs. GDP per capita, and put GDP per capita on a log scale. 

```{r dplyr 1.5}

```

# Exercise 2: Explore two variables with dplyr and ggplot2

## Part 1: Pick two quantitative variables to explore.

### Step 1: Make a summary table of the descriptives statistics for these variables 

```{r summary table}

```

### Step 2: Make a scatterplot of these variables 

```{r scatterplot}

```

## Part 2: Pick one categorical and one quantitative variable to explore. 

### Step 1: Make a summary table giving the sample size and descriptives statistics for the quantitative variable by group 

```{r summary table - sample size and descriptives}

```

### Step 2: Make a plot to visualize these variables.  

```{r plots}

```
