---
title: "Lab 3"
author: "Cassandra Richardson"
date: "4/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(palmerpenguins)
library(tidyverse)
library(gapminder)
```
# Before we get started, let's see what our data set looks like: 

```{r table}
View(gapminder)
``` 

# Exercise 1 

## Part 1: Filter gapminder to three countries of my choice:

```{r dplyr 1.1}
gapminder_three <- gapminder |> 
  filter((country == "Iceland" | country == "Italy" | country == "Switzerland") & year >= 1970, year < 1980)
 print(gapminder_three)
```

## Part 2: Same as above, then select "country" and "gdpPercap"

```{r dplyr 1.2}
gapminder_three <- gapminder |> 
  filter((country == "Iceland" | country == "Italy" | country == "Switzerland") & year >= 1970, year < 1980) |>
  select(country, gdpPercap)
  print(gapminder_three)
```

## Part 3: Create a new variable for the change in life expectancy from the previous measurement for that country. Then filter to only show countries that experienced a drop in life expectancy. 

```{r dplyr 1.3}
lifeExp_decrease <- gapminder|>
  group_by(country) |>
  mutate(lifeExp_decrease = lifeExp - lag(lifeExp)) |>
  filter(lifeExp_decrease < 0)
  print(lifeExp_decrease)
```

## Part 4: Filter gapminder to show the max GDP per capita for each country. 

```{r dplyr 1.4}
gapminder_maxGDP <- gapminder |>
  group_by(country) |> 
  mutate(maxGDP = max(gdpPercap)) |> 
  filter(maxGDP == gdpPercap)
  print(gapminder_maxGDP)
```

## Part 5: Create a scatterplot of Canda's life expectancy vs. GDP per capita, and put GDP per capita on a log scale. 

```{r dplyr 1.5.1}
Canada <- gapminder |> 
  filter(country == "Canada")
```
```{r dplyr 1.5.2}
ggplot(Canada) + 
  aes (x = lifeExp, y = gdpPercap) +
  geom_point() + 
  scale_x_continuous(trans = "log10")
  print(Canada)
```

# Exercise 2: Explore two variables with dplyr and ggplot2

## Part 1: Pick two quantitative variables to explore.

### Step 1: Make a summary table of the descriptives statistics for these variables 

```{r penguins}
penguin_data <- palmerpenguins::penguins
```

```{r summary table}
penguin_data |> 
  summarize(mean(body_mass_g, na.rm = T), sd(body_mass_g, na.rm = T), mean (bill_length_mm, na.rm = T), sd(bill_length_mm, na.rm = T))
```

### Step 2: Make a scatterplot of these variables 

```{r scatterplot}
ggplot(penguin_data) + 
  aes (x = body_mass_g, y = bill_length_mm) +
  geom_point() +
  geom_smooth()
```

## Part 2: Pick one categorical and one quantitative variable to explore. 

### Step 1: Make a summary table giving the sample size and descriptives statistics for the quantitative variable by group 

```{r summary table - sample size and descriptives}

```

### Step 2: Make a plot to visualize these variables.  

```{r plots}

```
