---
title: "Lab 02 - Plastic waste"
author: "Cassandra Richardson"
date: "3-10-2022"
output: html_document
---

## Load packages and data

```{r setup, message=FALSE}
library (tidyverse)
library (ggplot2)
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv(here::here("data/plastic-waste.csv"))
View(plastic_waste)
```

## Exercises

### Exercise 1
# Create a histogram showing the distribution of plastic waste per capita faceted by continent. It looks like Europe, North America, and Asia have the highest plastic waste per captia, whereas Oceania and South America have the least. 
```{r plastic-waste-continent}
ggplot(plastic_waste) +
  aes(x = plastic_waste_per_cap) +
  geom_histogram(binwidth = .2, fill = "blue") + 
  facet_wrap (~continent)

ggplot(plastic_waste) +
  aes(x = plastic_waste_per_cap, y = continent) +
  geom_density(aes(y = after_stat(count))) 

ggplot(plastic_waste) + 
  aes(x = plastic_waste_per_cap,
      color = continent, 
      fill = continent) + 
  geom_density(aplha = .1)
```

### Exercise 2

```{r plastic-waste-density}
# insert code here
```

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```

## Pro-Tips

### Excercise 3

Try this :D

```
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
```

### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements


