---
title: "Lab 6"
author: "Cassandra Richardson"
date: "4/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

songs <- read_csv("https://raw.githubusercontent.com/bwiernik/progdata-class/master/data/singer/songs.csv")
locations <- read_csv("https://raw.githubusercontent.com/bwiernik/progdata-class/master/data/singer/loc.csv")

(time <- as_tibble(songs) |> 
   rename(song = title))

(album <- as_tibble(locations) |> 
   select(title, everything()) |> 
   rename(album = release,
          song  = title))

#view(time)
#View(album)
```

# Exercise 1 - singer package 

## Question 1: For which of the songs in "time" do we know its corresponding album?

#### In order to match the songs in "time" with the albums in "album," we need to join the tables: 

```{r song and album}
time |> 
  inner_join(album, by = "song") 
```

#### In this code, I combined the two tables on the basis of having the same songs. This shows us that we know the corresponding album of 13 songs. 

## Question 2: Add the corresponding albums to "time", while keeping all rows even if the album information is not available. 

``` {r add albums to time}
time |>
  left_join(album, by = "song")
```

#### "left_join" prioritizes the first datset (i.e., time) and preserves all rows, while adding in the album data by matching songs. 

## Question 3: Which songs have year but not album information?

```{r year not album}
time |> 
  anti_join(album, by = "song")
```

#### In this function, I am returning all rows from "time" where there are NOT matching values in "album" because I want to filter out all the songs that we DO have album information for. This shows us that there are 9 songs from "time" that we have year information for, but not album information. 


## Question 4: Which artists are in "time" but not "album"?

```{r artists}
time |> 
  anti_join(album, by = "artist_name")
```
#### This function is the same as question 3, but instead of matching datasets on the basis of songs, I matched them on the basis of artist names. The only artist that is in "time" but not "album" is Mariah Carey. 

## Question 5: Merge the two tibbles

```{r merging}
time |> 
  full_join(album, by = "song")
```

#### By using "full_join" this returns all rows and all columns from both datsets, putting NA when there are not matching values. 


# Exercise 2 - LOTR 

```{r lotr setup, include=FALSE}
fell <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Fellowship_Of_The_Ring.csv")
ttow <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Two_Towers.csv")
retk <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Return_Of_The_King.csv")

#View(fell)
#View(ttow)
#View(retk)
```

## Question 1: Stack these three tibbles into one tibble. 

``` {r joining}
two_movies <- full_join(fell, ttow)

all_movies <- full_join(two_movies, retk)
```

#### I wasn't sure how to do this in one step. Instead, I first combined the tibbles for "fell" and "ttow" into a new tibble called "two_movies" using the "full_join" functions to preserve all rows and columns. Then I used "two_movies" and added the third movie tibble "retk"

## Question 2: Which races are in "The Fellowship of the Ring" but not in the other tibbles?

```{r races}
q2 <- fell |> 
  anti_join(ttow, by = "Race") |> 
  anti_join(retk, by = "Race")
```

#### By trying to use "anti_join" to return all races that are NOT matching with the races in "fell", this returned a tibble with 0 observations. There are 0 observations because the races in "fell" (i.e., elf, hobbit, man) were also all present in "ttow" and "retk"

# Exercise 3: Set operations 

```{r exercise 3 setup}
(y <-  tibble(x1 = LETTERS[1:3], x2 = 1:3))
(z <- tibble(x1 = c("B", "C", "D"), x2 = 2:4))
```

## Question 1: Show rows that appear in both "y" and "z"

```{r yz}
intersect(y, z)
```

#### The "intersect" function returns only the observations that are in both y and z

## Question 2: Make a dataset to reflect that day 1 in "y" was day 2 in "z"

```{r lag day one?}
union (
  mutate(y, day = "Day 1"),
  mutate(z, day = "Day 2")
)
```

#### This tibble has a new variable added, "day", to reflect the day that data was collected. The "union" function returns the unique observations in y and z

## Question 3: Removes z's rows from y
``` {r delete}
setdiff(y, z)
```

#### The "setdiff" function returns observations that are in y, but not in z. This removes all of z's rows from y. 
