---
title: "Lab 6"
author: "Cassandra Richardson"
date: "4/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

songs <- read_csv("https://raw.githubusercontent.com/bwiernik/progdata-class/master/data/singer/songs.csv")
locations <- read_csv("https://raw.githubusercontent.com/bwiernik/progdata-class/master/data/singer/loc.csv")

(time <- as_tibble(songs) |> 
   rename(song = title))

view(time)
View(album)
```

# Exercise 1 - singer package 

## Question 1: For which of the songs in "time" do we know its corresponding album?

### In order to match the songs in "time" with the albums in "album," we need to join the tables: 

```{r inner join}
time |> 
  inner_join(album, by = "song") 
```

## In this code, I combined the two tables on the basis of having the same songs. This shows us that we know the corresponding album of 13 songs. 

## Question 2: Add the corresponding albums to "time", while keeping all rows even if the album information is not available. 

``` {r }
time |>
  left_join(album, by = "song")
```

## "left_join" prioritizes the first datset (i.e., time) and preserves all rows, while adding in the album data by matching songs. 

##Question 3: Which songs have year but not album information?

```{r}

```

## Answer 

## Question 4: Which artists are in "time" but not "album"?

```{r}

```

## Question 5: Merge the two tibbles



# Exercise 2 - LOTR 

```{ r setup}
fell <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Fellowship_Of_The_Ring.csv")
ttow <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Two_Towers.csv")
retk <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Return_Of_The_King.csv")
```

## Question 1: Stack these three tibbles into one tibble. 

``` {r joining}

```

## Question 2: Which races are in "The Fellowship of the Ring" but not in the other tibbles?

```{r races}

```

# Exercise 3: Set operations 

## Question 1: Show rows that appear in both "y" and "z"

```{r yz}

```

## Question 2: Make a dataset to reflect that day 1 in "y" was day 2 in "z"

```{r lag day one?}

```

## Question 3: Removes z's rows from y
``` {r delete}

```
