---
title: "Lab 4"
author: "Cassandra Richardson"
date: "2/15/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library(gapminder)
library(tidyverse)

dictionary <- readr::read_csv(here::here("data", "green_dictionary.csv"))
green_data <- readr::read_csv(here::here("data", "green_data.csv")) 
```

# 1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). Is there anything unusual?

```{r examining data}
#View(green_data)
#View(dictionary)
```

## Through looking at the scales in the dictionary, I realized that some of the variables are coded as -1, meaning that they will need to be reverse-coded before conducting analyses. 

``` {r reverse coding}
reversed <- c("green2", "comp6", "comp7", "comp8", "comp9", "comp10", "intel7", "intel8", "intel9", "intel10", "open7", "open8", "open9", "open10")

green_data_fix <- green_data |>
  mutate_all(na_if, -99)
  
green_data_recoded <- green_data_fix |>
  mutate(across(
    all_of(reversed),
    \(x) recode(x, "5" = 1, "4" = 2, "3" = 3, "2" = 4, "1" = 5, "-99" = NA_real_))) 

View(green_data_recoded)
```

# 2. Compute total scores for the four scales. 

``` {r scale scores}
summary(green_data_recoded)

green_total_scores <- green_data_recoded |>
  rowwise() |>
  mutate(
    id = id, 
    green_total = mean(c_across(green1:green5), na.rm = T),
    compassion_total = mean(c_across(comp1:comp10), na.rm = T),
    openness_total = mean(c_across(open1:open10), na.rm = T),
    intel_total = mean(c_across(intel1:intel10), na.rm = T),
    .before = everything())
```
# 3. Rescale variables to be 0-100 instead of original scales. Name these variables *_pomp

```{r rescale}
green_data_rescaled <- green_total_scores |>
  mutate(
    across(green_total:intel_total,
    \(x) 100 * (x-1)/(5-1),
    .names = "{.col}_pomp"), 
    .before = everything())
```

# 4. Make plots for the distributions of the 4 pomp-scored variables

## Histogram for total score on green reputation: 

```{r green plots}
ggplot(green_data_rescaled) + 
  aes (x = green_total_pomp) +
  geom_histogram(binwidth = 1)
```

## Histogram for total score on compassion:

```{r compassion plots}
ggplot(green_data_rescaled) + 
  aes (x = compassion_total_pomp) +
  geom_histogram(binwidth = 1)
```

## Histogram for total score on openness to experiences: 

```{r openness plots}
ggplot(green_data_rescaled) + 
  aes (x = openness_total_pomp) +
  geom_histogram(binwidth = 1)
```

## Histogram for total score on intellectual curiosity:

```{r intel plots}
ggplot(green_data_rescaled) + 
  aes (x = intel_total_pomp) +
  geom_histogram(binwidth = 1)
```

# 5. Make scatterplots showing the relationship between green reputation and each personality trait. Include a trend line for students and non-students. What do these plots show? 

## Scatterplot for green reputation and compassion:

```{r plots green and compassion}
green_data_rescaled |>
  filter(!is.na(student)) |>
ggplot() +
  aes(x = compassion_total_pomp, y = green_total_pomp,
       fill = factor(student)) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Scatterplot for green reputation and openness:

```{r plots green and openness}
green_data_rescaled |>
  filter(!is.na(student)) |>
ggplot() +
  aes(x = openness_total_pomp, y = green_total_pomp,
       fill = factor(student)) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Scatterplot for green reputation and intellectual curiosity:

```{r plots green and intel}
green_data_rescaled |>
  filter(!is.na(student)) |>
ggplot() +
  aes(x = intel_total_pomp, y = green_total_pomp,
       fill = factor(student)) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Answer: These scatterplots show a positive linear relationship between personality traits (compassion, openness, and intellectual curiosity) and green reputation such that as the personality scores increase, green reputation scores also increase. There does not seem to be much of a diference between students and non-students, except with intellectual curiosity the trend lines intersect. 

# 6. Compare green reputation between students and non-students using a rainfall plot. 

```{r rainfall plot}
ggplot(na.omit(green_data_rescaled)) +
  aes(x = student, y = green_total_pomp,
      group = student, fill = student, color = student) +
  geom_jitter(height = .2, alpha = .2) +
  geom_boxplot(color = "black", alpha = .5, width = .3, size = .5) + 
  ggdist::stat_slab(height = .3, color = "black", size = .2, aplha = .2, position = position_nudge(y = .2))
```

# 7. Compute a summary table of means, SD, medians, minima, and maxmima for the four scores, for students and nonstudents. 

## Summary table for openness, by student status (1 = not a student, 2 = student):

```{r openness summary}
openness_summary <- green_data_rescaled |>
  drop_na () |>
  group_by (student) |>
  summarize (mean = mean(openness_total_pomp),
             sd = sd(openness_total_pomp),
             min = min(openness_total_pomp),
             max = max(openness_total_pomp))
print(openness_summary)
```

## Summary table for compassion, by student status (1 = not a student, 2 = student):

```{r compassion summary}
comp_summary <- green_data_rescaled |>
  drop_na () |>
  group_by (student) |>
  summarize (mean = mean(compassion_total_pomp),
             sd = sd(compassion_total_pomp),
             min = min(compassion_total_pomp),
             max = max(compassion_total_pomp))
print(comp_summary)
```

## Summary table for intellectual curiosity, by student status (1 = not a student, 2 = student):

```{r intel summary}
intel_summary <- green_data_rescaled |>
  drop_na () |>
  group_by (student) |>
  summarize (mean = mean(intel_total_pomp),
             sd = sd(intel_total_pomp),
             min = min(intel_total_pomp),
             max = max(intel_total_pomp))
print(intel_summary)
```